### 2017-12-29 README.Rmd

---
output:
  github_document:
    toc: true 
    toc_depth: 3
---

Infer: an R package for tidyverse-friendly statistical inference

---
[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)

@@

# Installation

To install the current stable version of `infer`, make sure to install `devtools` first:

```
install.packages("devtools")
devtools::install_github("andrewbpray/infer")
```

To install the development version of `infer` (with `devtools` installed already):

```
devtools::install_github("ismayc/infer", ref = "dev")
```

## Hypothesis tests
![](figs/ht-diagram.png)

#### Randomization-based Examples

@@

```
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
         vs = factor(vs),
         am = factor(am),
         gear = factor(gear),
         carb = factor(carb))
```

Check the package vignettes for further examples using theory-based methods
in combination with randomization-based methods.

***

### One numerical variable (mean)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", mu = 25) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "mean")
```

### One numerical variable (median)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", med = 26) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "median")
```

### One numerical variable (standard deviation)

```
mtcars %>%
  specify(response = mpg) %>% # alt: mpg ~ NULL (or mpg ~ 1)
  hypothesize(null = "point", sigma = 5) %>% 
  generate(reps = 100, type = "bootstrap") %>% 
  calculate(stat = "sd")
```

### One categorical (2 level) variable

```
mtcars %>%
  specify(response = am) %>% # alt: am ~ NULL (or am ~ 1)
  hypothesize(null = "point", p = c("1" = .25)) %>% 
  generate(reps = 100, type = "simulate") %>% 
  calculate(stat = "prop")
```

### Two categorical (2 level) variables

```
mtcars %>%
  specify(am ~ vs) %>% # alt: response = am, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props")
```

### One categorical (>2 level) - GoF

```
mtcars %>%
  specify(cyl ~ NULL) %>% # alt: response = cyl
  hypothesize(null = "point", p = c("4" = .5, "6" = .25, "8" = .25)) %>%
  generate(reps = 100, type = "simulate") %>%
  calculate(stat = "Chisq")
```

### Two categorical (>2 level) variables

```
mtcars %>%
  specify(cyl ~ am) %>% # alt: response = cyl, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "Chisq")
```

### One numerical variable, one categorical (2 levels) (diff in means)

```
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in means")
```

### One numerical variable one categorical (2 levels) (diff in medians)

```
mtcars %>%
  specify(mpg ~ am) %>% # alt: response = mpg, explanatory = am
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in medians")
```

### One numerical one categorical (>2 levels) -  ANOVA

```
mtcars %>%
  specify(mpg ~ cyl) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "F")
```

### Two numerical vars - SLR

```
mtcars %>%
  specify(mpg ~ hp) %>% # alt: response = mpg, explanatory = cyl
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "slope")
```

## Confidence intervals

### One numerical (one mean)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "mean")
```

### One numerical (one median)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "median")
```

### One numerical (standard deviation)

```
mtcars %>%
  specify(response = mpg) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "sd")
```

### One categorical (one proportion)

```
mtcars %>%
  specify(response = am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "prop", success = "1")
```

### One numerical variable one categorical (2 levels) (diff in means)

```
mtcars %>%
  specify(mpg ~ am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means")
```

### Two categorical variables (diff in proportions)

```
mtcars %>%
  specify(am ~ vs) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in props")
```

### Two numerical vars - SLR

```
mtcars %>%
  specify(mpg ~ hp) %>% 
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "slope")
```

>>>>

---
output: github_document
---

#Infer

------------------------------------------------------------------------

[![Travis-CI Build Status](https://travis-ci.org/andrewpbray/infer.svg?branch=master)](https://travis-ci.org/andrewpbray/infer)

@@

```{r diagram, echo=FALSE}
knitr::opts_chunk$set(eval = FALSE)
knitr::include_graphics("https://raw.githubusercontent.com/andrewpbray/infer/master/figs/ht-diagram.png")
```

### Installation

------------------------------------------------------------------------

To install the current stable version of `infer`, make sure to install `remotes` first:

```{r}
install.packages("remotes")
remotes::install_github("andrewpbray/infer")
```

### Examples

------------------------------------------------------------------------

@@

```{r}
mtcars <- as.data.frame(mtcars) %>%
  mutate(cyl = factor(cyl),
          vs = factor(vs),
          am = factor(am),
          gear = factor(gear),
          carb = factor(carb))
```

Hypothesis test for a difference in proportions:

```{r}
mtcars %>%
  specify(am ~ vs) %>% # alt: response = am, explanatory = vs
  hypothesize(null = "independence") %>%
  generate(reps = 100, type = "permute") %>%
  calculate(stat = "diff in props")
```

Confidence interval for a difference in means:

```{r}
mtcars %>%
  specify(mpg ~ am) %>%
  generate(reps = 100, type = "bootstrap") %>%
  calculate(stat = "diff in means")
```
